\section{Computational picture for finite unions when \texorpdfstring{$m=3$}{m=3}}
\label{sec:m3-computational-picture}

Let
\[
    M_N(3)=\sup\{\mu(A): A\subset\T\text{ is a union of at most }N
    \text{ intervals and is }3\text{-sum-free}\}.
\]
The elementary one-interval construction gives \(M_1(3)=1/5\), and
Section~\ref{sec:closed-two-interval-proof} proves the sharp upper bound
\(M_2(3)=1/5\).  The MILP described in Section~\ref{sec:milp-formulation} has
reported the same optimum for \(N\leq8\).  The runs become expensive quickly:
the reported \(N=8\) computation took several hours.

A fresh profile of all 32 legal formulation-and-cut configurations for
\(N=5\) returned objective and dual bound \(1/5\) with zero MIP gap in every
case.  The two configurations singled out by the older profile reproduced
the same branch-and-bound node counts, 4,329 and 9,475, although wall times
changed with machine load.  The complete matrix, logs, problems, and solutions
are archived in
\code{json_results/verification_20260716/m3_profile_32/}.

\subsection{The naive LP relaxation}

Replacing every integer lift \(n_{ij\ell}\) by a continuous variable does not
expose the \(1/5\) bound.  Fresh LP runs for \(1\leq N\leq8\) returned
\[
    \min\{N/5,1\},
\]
both with and without the redundant interval-width cuts.  Thus the direct
relaxation is already non-sharp for \(N=2\); a useful dual argument will need
additional valid inequalities or a different formulation.  All 16 problems
and solutions are archived in
\code{json_results/verification_20260716/m3_lp_relaxation/}.

\subsection{Symmetry normalization and removable interactions}

In the translated-missing-point model, a reported useful normalization is:
\begin{itemize}
    \item the first interval starts at \(0\) and is chosen to be shortest;
    \item after reflection, the second interval is no longer than the last.
\end{itemize}
Under these assumptions, experiments ask which terms
\(I_i+I_j-3I_\ell\) can be dropped while the relaxed model still has optimum
\(1/5\).  This is a deliberately stronger statement than solving the full
model: if the relaxation still proves the same upper bound, then the omitted
terms were not needed for that numerical certificate.

The rerun archived in
\code{json_results/verification_20260716/removable_interactions/} makes the
scope of this evidence precise.  For \(N=2\), the exhaustive search found two
maximal families, each consisting of one triple.  For \(N=3\), it found seven
maximal families: five of size three and two of size four.  For \(N=4\), all
single-triple exclusions were tested and 16 were removable; a capped search
then found five maximality-checked families, of sizes
\(7,7,7,7,8\), but did not enumerate every maximal family.  For \(N=5\), 32
single triples were removable, but the bounded family search timed out before
finding a maximal family.  Thus only the \(N=2,3\) family lists are exhaustive.
The \(N=2,3\) search used the basic translated model, while the more expensive
\(N=4,5\) search added the redundant interval-width cuts.
The script \code{find_excludable_sum_free_triples.py} performs these searches
and records explicitly whether an enumeration completed.

The historical variant that also imposed the previously computed \(1/5\)
bound on every \((N-1)\)-component subunion was rerun separately.  It
reproduced the same two and seven exhaustive families for \(N=2,3\), the same
five capped families for \(N=4\), and the same count of 32 removable single
triples with no family found before timeout for \(N=5\).  Thus that extra
inductive cut does not enlarge the established scope: its \(N=4,5\) family
searches are still partial.  The commands and reports are archived in
\code{json_results/verification_20260716/removable_interactions_subset_bound/}.

For two intervals \(I,J\), the endpoint proofs below explain why numerical
redundancy must be handled carefully.  A five-term covering argument can leave
a single artificial endpoint.  In the \(R_5\)-first proof, the term
\(J+J-3J\) removes the configuration
\[
    I=(0,1/10),\qquad J=(1/4,7/20),
\]
while in the alternative \(R_6\)-first proof, the term \(I+J-3J\) removes the
configuration
\[
    I=(0,9/65),\qquad J=(15/65,19/65).
\]
Thus an interaction may be unnecessary on an open region of parameter space
yet still be essential at one boundary point.
