\section{Computational experiments for higher multipliers}
\label{sec:other-multipliers}

The experiments for \(m\geq4\) show that a single interval is generally not
extremal.  The explicit certificates in Section~\ref{sec:explicit-m4-m5}
establish
\[
    d_4(\T)\geq\frac{11}{64}>\frac16,
    \qquad
    d_5(\T)\geq\frac6{35}>\frac17,
\]
and the rational reconstructions produced by the fresh runs give the further
exact bounds
\[
    d_8(\T)\geq\frac{49}{320}>\frac3{20},
    \qquad
    d_9(\T)\geq\frac{136}{891}>\frac5{33},
\]
and
\[
    d_{12}(\T)\geq\frac{251}{1728}>\frac17,
    \qquad
    d_{13}(\T)\geq\frac{122}{845}>\frac{28}{195}.
\]
The \(m=12\) bound comes from seven intervals: the equally spaced base and
three short additions.  It supersedes the earlier six-interval value
\(73/504\).  Exact arithmetic also verifies the systematic bounds
\[
 d_m(\T)\geq
 \frac{m^3+4m^2+8m-64}{8m^2(m+2)}
 \quad(4\mid m,\ 16\leq m\leq100)
\]
and
\[
 d_m(\T)\geq
 \frac{m^3+4m^2+7m-36}{8m^2(m+2)}
 \quad(m\equiv1\!\!\pmod4,\ 13\leq m\leq97).
\]
These are finite, exactly checked families rather than claims about all
members of the two congruence classes.  Their endpoint formulas and the more
than \(2.28\) million exact lifted-image checks are described in
Section~\ref{sec:extra-intervals}.

For \(m=5\), fresh standard-model runs with at most five and at most six
intervals both returned the same density \(6/35\), with zero reported MIP gap.
The six-interval run used four positive intervals, each of length \(3/70\),
and two zero-length intervals.  After rational reconstruction, its four
components form exactly the twofold preimage, under \(x\mapsto2x\), of the
reconstructed two-component solution from the five-interval run.  This is the
previously observed four-component splitting, and exact arithmetic verifies
both reconstructed forms as constructions.  The equality of the two finite
model optima remains numerical; it is not an upper-bound proof for arbitrary
measurable sets.

For two intervals, the observed formula is
\begin{equation}
    M_2(m)=\frac{2(m-2)}{m(m+2)},\qquad m\geq4,
    \label{eq:two-interval-conjecture}
\end{equation}
where the restriction \(m\geq4\) is essential because the proved value for
\(m=3\) is \(1/5\).  A zero-gap scan of every integer
\(4\leq m\leq100\) returned values agreeing with
Formula~\eqref{eq:two-interval-conjecture}; the largest numerical discrepancy
was less than \(7\times10^{-11}\).  This largest discrepancy came from the
saved \(m=87\) point, whose constraint replay had a residual of about
\(6.1\times10^{-9}\), within the solver's default feasibility tolerance.  A
rerun with \(10^{-10}\) feasibility tolerances reduced the largest residual to
less than \(3\times10^{-14}\) and agreed with the formula to less than
\(4\times10^{-16}\).  The formula is the \(q=2\) case of the equally spaced
construction in Section~\ref{sec:equally-spaced-construction}.  No general
two-interval upper bound proving~\eqref{eq:two-interval-conjecture} is currently
included.  The full problems and solutions are archived in
\code{json_results/verification_20260716/two_interval_scan/}, with the strict
rerun in the sibling directory \code{two_interval_scan_strict/}.
